---
title: "Project 4"
author: "Austin Sarney"
output: 
  html_document:
    code_folding: hide
  
---


```{css echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Cal+Sans&family=Micro+5&display=swap');

.author, .title, .subtitle, h2 {
    margin: 0px 0px 10px 0px;
}

.title {
    color: #FFF !important;
}

.author {
    background: linear-gradient(90deg,rgba(255, 0, 0, 1) 0%, rgba(255, 149, 0, 1) 20%, rgba(255, 229, 0, 1) 40%, rgba(0, 255, 149, 1) 60%, rgba(0, 47, 255, 1) 80%, rgba(191, 0, 255, 1) 100%);
    /* I had to put a gradient somewhere :) */
    background-clip: text;
    color: rgba(0,0,0,0);
    background-size: 100% 100%;
    background-repeat: no-repeat;
    display: block;
    width: max-content;
    margin: 0px 0px 10px 0px;
    font-family: "Micro 5", sans-serif;display: block;
    font-size: 40px; /* I do not know why Micro 5 looks so small by default */
    text-shadow: 2px -2px 0 rgba(255, 255, 255, 0.7);/* to make it readable */
}

body {background: #ECEBE4;} 

h1, h2, h3 {font-family: "Cal Sans", sans-serif;display: block; color: #49306B;}

div#header {
  background: #49306B !important;
  border-radius: 10px; 
  padding: 20px;
  margin: 20px;
}

div.section {
  background: rgba(255, 255, 255, 0.8);
  border-radius: 10px; 
  padding: 20px;
  margin: 20px;
  
  animation: slideIn ease-in-out both;
  animation-timeline: view();
  animation-range: entry 10% entry 30%;
  
}

html {
overflow-x: hidden;
}

.figcaption {
  color: #777;
}

@keyframes slideIn {
from {transform: translateX(50vw); background: rgba(73, 48, 107, 0.5)}
to {transform: translateX(0px); background: rgba(255, 255, 255, 0.8)}
}

@media (prefers-reduced-motion: reduce) {div.section, div#header {animation: none !important;}}
/* I hope the animation isn't too obnoxious for everyone else... */



```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

For this project, I worked with Armand Spencer to gather data about our commutes to and from university. 

We continued to use the same form as in project 2. our questions were: What method did you use? How many minutes did it take? and when did you start your commute?
These questions are useful because they give us enough information about the commutes without putting anything unnecessary that makes it hard to fill out the form (following guideline 2). The final question also follows guideline 4 because it validates that the value entered is a valid time.

I chose to take the `method` variable and instead use it as a variable that shows whether the commute was by Austin or Armand. We chose this question in case we added someone else to our group, but this didn't end up happening. Although this isn't guaranteed by the form, we know that all of the bus commutes were by me and all the car commutes were by Armand.

I chose to use geom_hist because it allowed me to set the `binwidth` which meant that the length would show up as a rounded value. This is much more useful than just unrounded values. I chose a geom_violin because it looked like it would be a good way of representing 1 discrete and 1 continuous variable. I chose geom_col because it allowed me to represent a discrete and continuous variable and showed a clear (even if small) decrease between the 2 categories.


## Visual data story

[Link to the visual data story](https://austin-540.github.io/stats220/Project%204/visual_data_story)


My visual data story shows creativity because I have used CSS to include my plots' colour pallete in the background of the report, and heading text colour, which makes the presentation feel more cohesive. My first 2 plots also link in a way where the second plot answers a question that you might wonder from looking at the first plot, as part of a more cohesive data story.


## Learning reflection

An important idea from module 4 is that we can use ggplot to add lots of different layers to plots to make them communicate what you want it to show. Each extra layer added to the plot to be better at communicating. I think this is especially true for scales and level labels because sometimes the target audience doesn't need to know specific details (like how "Austin" was a more useful label than "Car" for my data). 

I am curious about how we can use more dynamic adjustments in ggplot. Many of my adjustments were reliant on me knowing ahead of time what the data is, so it would be useful for a dynamic report to be able to make adjustments that can keep doing what you want even with unpredictable data.

## Appendix
```{r file='data_visualisation.R', eval=FALSE, echo=TRUE}

```
